A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-14 paper.tex
Remove the paper using IPFS + MAM

%TODO: cite IOTAIndustryMarketplace
\section{Related Work}
\label{section:relatedWork}
G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. The data validation and traceability are achieved via Ethereum smart contract. But data is plaintext on blockchain that the system is not appropriate for sensitive data.

@@

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. With encrypted data contents storing on IPFS, and add the encrypted IPFS link to MAM for further exchange. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold, and enable trading and perform access control on Ethereum smart contract. However, the details of trading and interactions between providers and consumers are not illustrated in this paper.

The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.

>>>>

\section{Related Work}
\label{section:relatedWork}
G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. The data validation and traceability are achieved via Ethereum smart contract. But data is plaintext on blockchain that the system is not appropriate for sensitive data.

@@

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the works above does not does not take into account the refund and unsubscribe mechanism of trading model.
